---
title: "Assignment02"
author: "Travis Green"
---

# Import a stata file into R

```{r}
library("haven")
TEDS_2016 <- read_dta ("https://github.com/datageneration/home/blob/master/DataProgramming/data/TEDS_2016.dta?raw=true")
```

# Generate frequency table of the Tondu variable

```{r}
library(descr)
freq(TEDS_2016$Tondu)
```

# Generate barchart of the Tondu variable

```{r}
library(ggplot2)
ggplot(TEDS_2016, aes(Tondu)) + 
  geom_bar()
```

```{r}
TEDS_2016$Tondu<-as.numeric(TEDS_2016$Tondu,labels=c("Unification now","Status quo,unif.infuture","Statusquo,decidelater","Statusquoforever","Statusquo,indep.infuture","Independencenow","No response"))
```

**What problems do you encounter when dealing with the dataset?**

There are no values for Tondu around the category of 7.5. Tondu referes to an attitude toward unification with mainland China.

**How to deal with missing values?**

We can drop observations with missing values or we can try to impute them (example: average imputation or common point imputation).

**Explore the relationship between Tondu and other variables including female, DPP, age, income, edu, Taiwanese and Econ_worse. What methods would you use?**

For numerical variables such as age, income and years of education, we can correlate them with Tondu or use scatterplots and a linear regression modeling. For categorical variables such as gender, DPP and Taiwanese in relationship to Tondu, we can use a bar plot.

**How about the votetsai variable (vote for DPP candidate Tsai Ing-wen)?**

Since votetsai is dychotomous, we can assume it to be a dependent variable, we can then use logit to analyze the effect of Tondu on whether a voter votes for Tsai Ing-wen or not.
